---
title             : "Prevalence of OCD in different patient groups"
short title       : "OCD patients information analysis"

author: 
  - name          : "Luchen Yu"
    affiliation   : "University of Chicago"
    email         : "ylc23@uchicago.edu"

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  One or two sentences to put the results into a more **general context**.
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : "r-references.bib"

floatsintext      : no
linenumbers       : yes
draft             : no
mask              : no

figurelist        : no
tablelist         : no
footnotelist      : no

classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
# load papaja package
library("papaja")
source("R code.R",local = knitr::knit_global())
r_refs("r-references.bib")
```

```{r helloworld, include = FALSE}
# call hello_world function
source("functions.R", local = knitr::knit_global())
```

```{r read OCDdata}
# load readr package
library(readr)

# read in the dataset
OCD.data <- read.csv("ocd_patient_dataset.csv")

# examine the dataset
str(OCD.data)

# each column is either a character or numeric number
# each row is a single observation for one patient
# each cell is a single measurement
# for research questions about the association of the prevalence of OCD with education level, family history of OCD, and previously diagnosed disorders, only the column "Education Level", "Family History of OCD", and "Previous Diagnoses" are needed, all the other columns are extraneous
```

```{r intermediate OCDdata}
# create an intermediate dataset
# select specific columns that are related to my research questions
library(dplyr)
select(OCD.data, Education.Level, Family.History.of.OCD, Previous.Diagnoses)

# keep rows based on certain column values
# High school as education level, has family history of OCD, and does not be previously diagnosed
filter(OCD.data, Education.Level == "High School" & Family.History.of.OCD == "Yes" & Previous.Diagnoses == "None")

# combine the two
# intermediate dataset for High school educated patients with family history of OCD and does not be diagnosed with other disorders before
intermediate.OCD.data <- OCD.data %>%
  select(Education.Level, Family.History.of.OCD, Previous.Diagnoses) %>%
  filter(Education.Level == "High School" & Family.History.of.OCD == "Yes" & Previous.Diagnoses == "None")

# write into csv filetype
csv_file_path <- "intermediate_ocd_data.csv"
write.csv(intermediate.OCD.data, csv_file_path)
```


```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# **Introduction**

<!-- Ordered list -->
I will analyze these three research questions below.  
1. Is there a significant difference in the prevalence of OCD among individuals with varying levels of education?  
2. Does the family history of OCD contribute to the development of the OCD disorder?  
3. Are patients previously diagnosed with other disorders more likely to develop OCD?

<!-- Unordered list -->
I will analyze from three aspects.  
* Association of education level with prevalence of OCD.  
* Association of family history of OCD with prevalence of OCD.  
* Association of previously diagnosed disorders with prevalence of OCD.  

<!-- Linked URL -->
[My GitHub](https://github.com/luchen0805/OCD)

# **Methods**

# **Data analysis**
We used `r cite_r("r-references.bib")` for all our analyses.

## ***Association of education level with prevalence of OCD***

### Is there a significant difference

## ***Association of family history of OCD with prevalence of OCD***

## ***Impact of previously diagonsed disorders on prevalence of OCD***

# **Results**

# **Discussion**


\newpage

# **References**

::: {#refs custom-style="Bibliography"}
:::
